Handling Recursion in Generic Programming Using Closed Type Families

### 2018-04-26 lncs-paper.tex
Polish

One possible solution to the aforementioned shortcoming of SOP is to modify the its core by explicitly encoding recursive positions using the fixed-point approach. However, this may complicate the whole framework significantly. Besides, such a decision may lead to extra conversions between the generic views.

>>>>

One possible solution to the aforementioned shortcoming of SOP is to modify its core by explicitly encoding recursive positions using the fixed-point approach. However, this may complicate the whole framework significantly. Besides, such a decision may lead to extra conversions between the generic views.
